A scenario for a Planckian standard kilogram

### 2017-10-24 manuscript_gravitationalconstant.tex
minor changes in literature references

\bibitem{Chao15} L.S. Chao, S. Schlamminger, D.B. Newell, J.R. Pratt, F. Seifert, X. Zhang, G. Sineriz, M. Liu and D. Haddad, ``A LEGO Watt balance: An apparatus to determine a mass based on the new SI", \textit{American Journal of Physics}, 83:11:913--922 (August 2015).

@@

\bibitem{Quinn14} T. Quinn, C. Speake, H. Parks and R. Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014).

\bibitem{Newman14} R. Newman, M. Bantel, E. Berg and W. Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (September 2014).

\bibitem{Luo09} J. Luo, W. Liu, L. Tu, C. Shao, L.Liu, S. Yang, Q. Li and Y. Zhang, ``Determination of the Newtonian gravitational constant $G$ with time-of-swing method'', \textit{Phys. Rev. Lett.}, 102:240801 (June 2009).

\bibitem{Schlamminger06} S. Schlamminger, E. Holzschuh, W. Kündig, F. Nolting, R.E. Pixley, J. Schnurr and U. Straumann, ``Measurement of Newton's gravitational constant", \textit{Phys. Rev. D}, 74:082001 (October 2009).

\bibitem{Parks10} H.V. Parks and J.E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (September 2010).

\bibitem{Rosi14} G. Rosi, F. Sorrentino, L. Cacciapuoti, M. Prevedelli and G.M. Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518-521 (June 2014).

@@

\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, and P. Cassey, and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
Psychonomic Bulletin {\&} Review, 1--12 (2016).

\bibitem{Loughridge13} R. Loughridge, and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
American Control Conference, 3686--3703 (2013).

\bibitem{corner} Daniel Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
The Journal of Open Source Software (10), (2016).

\bibitem{CODATA16} P.J. Mohr, D.B. Newell and B.N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (July 2016).

>>>>

\bibitem{Chao15} L. S. Chao, S. Schlamminger, D. B. Newell, J. R. Pratt, F. Seifert, X. Zhang, G. Sineriz, M. Liu and D. Haddad, ``A LEGO Watt balance: An apparatus to determine a mass based on the new SI", \textit{American Journal of Physics}, 83:11:913--922 (2015).

@@

\bibitem{Quinn14} T. Quinn, C. Speake, H. Parks and R. Davis, ``The BIPM measurements of the Newtonian constant of gravitation $G$'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (2014).

\bibitem{Newman14} R. Newman, M. Bantel, E. Berg and W. Cross, ``A measurement of $G$ with a cryogenic torsion pendulum'', \textit{Philosophical Transactions of the Royal Society of London A: Mathematical, Physical and Engineering Sciences}, 372(2026) (2014).

\bibitem{Luo09} J. Luo, W. Liu, L. Tu, C. Shao, L. Liu, S. Yang, Q. Li and Y. Zhang, ``Determination of the Newtonian gravitational constant $G$ with time-of-swing method'', \textit{Phys. Rev. Lett.}, 102:240801 (2009).

\bibitem{Schlamminger06} S. Schlamminger, E. Holzschuh, W. Kündig, F. Nolting, R. E. Pixley, J. Schnurr and U. Straumann, ``Measurement of Newton's gravitational constant", \textit{Phys. Rev. D}, 74:082001 (2009).

\bibitem{Parks10} H. V. Parks and J. E. Faller, ``Simple pendulum determination of the gravitational constant", \textit{Phys. Rev. Lett.}, 105:110801 (2010).

\bibitem{Rosi14} G. Rosi, F. Sorrentino, L. Cacciapuoti, M. Prevedelli and G. M. Tino, ``Precision measurement of the Newtonian gravitational constant using cold atoms", \textit{Nature}, 510:518--521 (2014).

@@

\bibitem{vanRavenzwaaij16} D. van Ravenzwaji, P. Cassey and S. D. Brown, ``A simple introduction to Markov Chain Monte-Carlo sampling,'' 
Psychonomic Bulletin {\&} Review, 1--12 (2016).

\bibitem{Loughridge13} R. Loughridge and D. Y. Abramovitch, ``A tutorial on laser interferometry for precision measurements,'' 
American Control Conference, 3686--3703 (2013).

\bibitem{corner} D. Foreman-Mackey, ``corner.py: Scatterplot matrices in Python,'' 
The Journal of Open Source Software (10), (2016).

\bibitem{CODATA16} P. J. Mohr, D. B. Newell and B. N. Taylor, ``CODATA recommended values of the fundamental physical constants: 2014*, \textit{Reviews of Modern Physics}, 88(3):035009 (2016).
